### 2014-11-11 contract-language.tex
Quantifying cureff in weaker-than relation

\begin{definition}
A contract $\cv_{op}$ is said to be weaker than $\cv_{st}$ (written $\cv_{op}
\le \cv_{st}$ ) if and only if $\Delta \vdash \cv_{st} \Rightarrow \cv_{op}$.
\end{definition}

The $\Delta$ referred in the above definition is a conjunction of assumptions
about the nature of primitive relations. A \emph{well-formed} axiomatic
execution ($\E$) is expected to satisfy these assumptions (i.e., $\E \models
\Delta$).

>>>>

\begin{definition}
A contract $\cv_{op}$ is said to be weaker than $\cv_{st}$ (written $\cv_{op}
\le \cv_{st}$ ) if and only if $\Delta \vdash \forall \cureff.
\cv_{st} \Rightarrow \cv_{op}$.  
\end{definition}

The quantifier in the sequent binds $\cureff$ that occurs free in $\cv_{st}$ and
$\cv_{op}$. Context ($\Delta$) of the sequent is a conjunction of assumptions
about the nature of primitive relations. A \emph{well-formed} axiomatic
execution ($\E$) is expected to satisfy these assumptions (i.e., $\E \models
\Delta$).
